### 2018-02-13 thermoelectricity/paper.tex
final version

	To visualize the data with the open-circuited terminals, temperature difference was plotted against the input power. Uncertainties were propagated using the method of quadratures.

	\paperfig{PartOne}{\pdf{1}}{Temperature difference plotted against the power for the open-circuited terminals. The error bars were included but were too small to be visible. Linear functions were fitted to the two curves in the graph. The reciprocals of their slopes are the thermal conductances between the relevant materials. The thermal conductance between the two reservoirs, $K_d$, was found to be $(0.59\pm.06)\si{\watt\per\kelvin}$. This fit had a reduced $\chi^2$ of 24.2124 and an $R^2$ value of 0.962248. The thermal conductance between the output heat sink and the ambient, $K_{hs}$, air was found to be $(7.1\pm.9)\si{\watt\per\kelvin}$. This fit had a reduced $\chi^2$ of 0.307025 and an $R^2$ value of 0.933316.}\vspace{2em}

@@

	\paperfig{partTwoa}{\pdf{part2a-data}}{Power and temperature difference plotted against time. Uncertainties were included but were too small to be visible. An increasing exponential function with a plateau was fit to the temperature difference. The plateau was determined to have a height of $(37.3\pm.2)\si{\kelvin}$. This fit had a reduced $\chi^2$ of 20.3006 and an $R^2$ value of 0.994558.}

@@

	By examining the derivative of $P_{in}$ with an output temperature of $\SI{35}{\celsius}$ and an input temperature not exceeding $\SI{5}{\celsius}$, the optimum input current was determined using the TEC model. It is known that $P_{in}$ obeys the following relation.

>>>>

	To visualize the data with the open-circuited terminals, temperature difference was plotted against the input power. Uncertainties were propagated using the method of quadratures.\\

	\paperfig{PartOne}{\pdf{1}}{Temperature difference plotted against the power for the open-circuited terminals. The error bars were included but were too small to be visible. Linear functions were fitted to the two curves in the graph. The reciprocals of their slopes are the thermal conductances between the relevant materials. The thermal conductance between the two reservoirs, $K_d$, was found to be $(0.59\pm.06)\si{\watt\per\kelvin}$. This fit had a reduced $\chi^2$ of 24.2124 and an $R^2$ value of 0.962248. The thermal conductance between the output heat sink and the ambient, $K_{hs}$, air was found to be $(7.1\pm.9)\si{\watt\per\kelvin}$. This fit had a reduced $\chi^2$ of 0.307025 and an $R^2$ value of 0.933316. Residuals for the fits are shown below the plot.}\vspace{2em}

@@

	\paperfig{partTwoa}{\pdf{part2a-data}}{Power and temperature difference plotted against time. Uncertainties were included but were too small to be visible. An increasing exponential function with a plateau was fit to the temperature difference. The plateau was determined to have a height of $(37.3\pm.2)\si{\kelvin}$. This fit had a reduced $\chi^2$ of 20.3006 and an $R^2$ value of 0.994558. Residuals for the fit are shown below the plot.}

@@

	By examining the derivative of $P_{in}$ with an output temperature of $\SI{35}{\celsius}$ and an input temperature not exceeding $\SI{5}{\celsius}$, the optimum input current was determined using the TEC model. It is known that $P_{in}$ obeys the following relation.\columnbreak
